Supplementary Information: Improving Monocular Depth Estimation with Global Depth Histogram Matching

### 2019-10-18 paper/cvpr2020/sections/discussion.tex
pass over simulated results section

short summary

@@

\begin{itemize}
	\item laser power vs range tradeoff; may be limited to short--medium range
	\item if the monocular depth estimation fails, so will the histogram matching 
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}

>>>>

In summary, we demonstrate a method to greatly improve depth estimates from
monocular depth estimators by correcting the scale ambiguity errors inherent
with such techniques.  Our approach produces depth maps with accurate absolute
depth, and helps the generalization of neural networks for MDE across scene
types, including on data captured with our hardware prototype.  Moreover, we
require only minimal additional sensing hardware; we show that a single measurement
histogram from a diffused SPAD sensor contains enough information about global
scene geometry to correct errors in monocular depth estimates.

@@

Since our method relies on the monocular depth estimate, the accuracy of the
output depth map also relies on the performance of the initial depth estimate.
The demonstrated results show that when the MDE technique produces a depth map
with good ordinal depth, where the ordering object depth is roughly correct, the
depth estimate can be corrected to produce accurate absolute depth. However,
errors in the ordinal depth may not necessarily be corrected in the histogram
matching procedure and so may propagate to the final output depth map.

Additionally, since our method relies on a diffused pulsed laser, the laser
power is spread out over the entire scene. So for distant scene points, very
little light will return to the SPAD, and it may be difficult to accurately
capture distant scene geometry in the histogram. Thus our method will likely be
best suited to short to medium-range scenes.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Future Work}
While our hardware prototype is very large, future work could be done to
miniaturize this system. Our algorithm or similar sensor fusion algorithms could
also be integrated into electronics that already contain the required hardware
components, for example, existing cell phones with single-pixel SPAD
proximity sensors and RGB cameras.

Other methods for extracting scene information from the SPAD histogram could be
also employed, including learning-based methods to combine the MDE and
histogram. One might even consider sensing regimes where the number of
returning signal photons is very low, such as when the SPAD and camera operate
at high framerates. While most MDE techniques are tailored to clean RGB images,  
the SPAD histogram could potentially be used to help MDE
techniques generalize to noisy scenes under low-light conditions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Conclusions}
Neural network-based approaches to monocular depth estimation have yielded
significant improvements over the past several years for this task. However,
recently, such improvements have generally relied on new network architectures or
revised training procedures and have produced only modest improvements. Computational
photography approaches may provide the measurements needed to achieve much greater
performance improvements, especially as the sensors in devices we use every day
become more diverse, complex, and increasingly rely on techniques based on
sensor fusion and sophisticated computational algorithms.

%\begin{itemize}
%	\item new depth estimation CNNs achieve marginal gains, let's think about computational photography approaches that augment the measurements to achieve better performance
%	\item ...
%\end{itemize}

### 2019-10-18 paper/cvpr2020/sections/introduction.tex

%Estimating depth from images is an important open problem with applications to robotics, autonomous driving, and medical imaging. Dense depth maps are useful precursors to higher-level scene understanding tasks such as pose estimation and object detection.

Depth sensing is vital for the success of many computer vision tasks, such as navigation~\cite{geiger2013vision}, robotic vision, semantic segmentation~\cite{ren2012rgb,silberman2012indoor,gupta2013perceptual}, 3D object detection~\cite{shrivastava2013building,lin2013holistic,gupta2014learning,song2014sliding,song2016deep}, and 3D object classification~\cite{wu20153d,maturana2015voxnet,qi2016volumetric}. However, traditional depth sensing techniques require multiple cameras, active illumination, camera motion, or other aspects that may make their deployment challenging.

One of the most promising approaches to overcoming these challenges is monocular depth estimation (MDE)~\cite{Saxena2006,Eigen2014,Laina2016,Fu2018,Alhashim2018}. Given a single RGB image, a monocular depth estimator uses pictorial cues in the image, such as perspective, occlusion, shading, and relative object size, to predict a dense depth map of the scene. While neural networks solving the MDE problem have significantly improved over the last years, this remains an ill-posed inverse problem with inherent scale ambiguity. Pictorial cues alone allow for the ordinal depth, that is the relative ordering of objects in a scene, to be robustly estimated~\cite{Eigen2014,Fu2018}. However, MDE approaches to date are incapable of reliably estimating absolute distances of a scene. Interestingly, Alhashim and Wonka~\cite{Alhashim2018} recently showed that if the MDE network has oracle access to the ground truth median scene depth, then correcting the output of the estimator to match this median depth produces accurate absolute depth maps.

@@

While access to ground truth depth is impossible in a realistic scenario, one of our primary insights is that low-cost sensors capable of capturing aggregated depth information of a scene are readily available and already part of the sensor suite of many cellphones. These proximity sensors, for example deployed in Apple's iPhones, contain a low-power pulsed light source and a single-pixel, single-photon avalanche diode (SPAD) to sense the distance of one ray direction in front of the camera. Coupled with high-power laser sources, SPADs also form the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,pawlikowska2017single,Li:2019}. Whereas individual SPADs are easy to fabricate and sufficiently cost effective to be deployed in consumer electronics, the required ultra-fast time-stamping electronics make it difficult to fabricate high-resolution SPAD arrays at low cost. A single or a few SPADs could certainly be used together with a raster scanning mechanism, which is typical for LiDAR systems, but the mechanical complexity of such a system prevents usage in mobile devices and the inherent tradeoff between scan speed and resolution makes it difficult to capture high-resolution depth maps at high framerates.

Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way. Rather than optically focusing them to record the distance along one ray, we diffuse the emitted light and the detector over the entire scene. This allows us to directly capture the integrated depth of the scene---a depth histogram. Technically, a diffused SPAD does not record a true depth histogram but a transient that is affected by square-distance falloff of the backscattered light, spatially varying reflectance of the scene, ambient photons, and detector noise. However, we can interpret the measurements of a single-pixel SPAD as something similar to a depth histogram while keeping in mind that they are not exactly the same.

@@

In this paper, we develop a sensor fusion strategy that processes the ordinal depth computed by some monocular depth estimator to match the output of the diffused SPAD. With extensive simulations, we demonstrate that our approach achieves substantial improvements in the quality of the estimated depth maps, comparable to the oracle median depth, disregarding which specific depth estimator is used. Moreover, we build an RGB-SPAD camera prototype and again demonstrate that our sensor fusion strategy achieves significantly higher-quality depth maps for a variety of captured scenes than a monocular depth estimator alone. With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware. Specifically, we make the following contributions:
%
\begin{itemize}
	\item We introduce the idea of augmenting an RGB camera with a global depth histogram captured by a SPAD to address scale ambiguity error in monocular depth estimators.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype RGB-SPAD camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

>>>>

Estimating dense 3D geometry from 2D images is an important open problem with applications to robotics, autonomous driving, and medical imaging. Depth maps are a common representation of scene geometry and are useful precursors to higher-level scene understanding tasks such as pose estimation and object detection. Additionally, many computer vision tasks rely on depth sensing, including navigation~\cite{geiger2013vision}, semantic segmentation~\cite{gupta2013perceptual,ren2012rgb,silberman2012indoor}, 3D object detection~\cite{gupta2014learning,lin2013holistic,shrivastava2013building,song2014sliding,song2016deep}, and 3D object classification~\cite{maturana2015voxnet,qi2016volumetric,wu20153d}.

Traditional depth sensing techniques include those based on stereo or multiview, active illumination, camera motion, or focus cues~\cite{szeliski2010computer}. However, each of these techniques has aspects that may make their deployment challenging. For example, stereo or multiview techniques require multiple cameras, active illumination techniques may have limited resolution or require time-consuming scanning procedures, and other techniques require camera motion or multiple exposures at different focus distances.

One of the most promising approaches to overcoming these challenges is monocular depth estimation (MDE), which requires only a single RGB image from a conventional camera to recover a dense depth map~\cite{Alhashim2018,Eigen2014,Fu2018,Laina2016,Saxena2006}. Recent approaches to MDE employ neural network models that learn to predict depth by exploiting monocular image cues such as perspective, occlusion, shading, and relative object size. While such models have significantly improved over recent years, MDE approaches to date are incapable of reliably estimating absolute distances in a scene due to the inherent scale ambiguities of monocular image cues. Instead, these models excel in predicting ordinal depth, or the relative ordering of objects in a scene~\cite{Eigen2014,Fu2018}. Interestingly, Alhashim and Wonka~\cite{Alhashim2018} recently showed that if the median ground truth depth of the scene is known, the initial output of a MDE network can be corrected to produce accurate absolute depth.

@@

\begin{figure}
  \includegraphics[width=\linewidth]{teaser.pdf}
  \caption{Monocular depth estimation predicts a depth map (upper right) from a single RGB image (upper left). The ill-posedness of the problem prevents reliable absolute depth estimation, resulting in large errors (inset image). The proposed method uses a measurement from a diffused SPAD (lower left), which resembles the shape of a histogram of the ground truth depth map, to correct the output of the depth estimation and optimize the quality of the estimated absolute depth (lower right).}
  \label{fig:teaser}
\end{figure}

Although access to the median ground truth depth is impossible in a realistic scenario, low-cost sensors capable of capturing aggregated depth information from a scene are readily available. For example, the proximity sensor on recent generation Apple iPhones uses a low-power pulsed light source and a single-pixel, single-photon avalanche diode (SPAD) to sense distance to an object directly in front of the phone. SPADs have also been used to recover full 3D geometry, forming the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,Li:2019,pawlikowska2017single}. However, SPADs have not been used for 3D imaging on consumer electronics because the requirement for ultra-fast timing electronics makes it difficult to produce high-resolution arrays at low cost, and because the scanning requirement for single-pixel systems introduces a point of mechanical failure and complicates high-resolution, high-framerate imaging.

%Individual SPADs are easy to fabricate and sufficiently cost-effective to be deployed in consumer electronics. When coupled with high-power pulsed lasers, they also form the backbone of emerging single-photon LiDAR systems~\cite{Kirmani:2014,pawlikowska2017single,Li:2019}. However, the required ultra-fast time-stamping electronics make it difficult to fabricate high-resolution SPAD arrays at low cost. Moreover, the scanning requirement for single-pixel systems precludes high-resolution, high-framerate depth mapping and is a barrier to integration in small consumer electronics.

Here, we propose to use a single-pixel SPAD and pulsed light source in an unconventional way: rather than optically focusing them to record the distance to a single scene point, we diffuse the emitted light and the detector over the entire scene. The resulting measurement resembles a histogram of the depth of the scene and can be used to achieve accurate absolute depth when combined with a monocular depth estimate (\cf~Figure~\ref{fig:teaser}).

%Technically, a diffused SPAD does not record a true depth histogram, but a transient that is affected by square-distance falloff of the backscattered light, spatially varying reflectance of the scene, ambient photons, and detector noise. Nevertheless, we can interpret the measurements of a single-pixel SPAD as something similar to a depth histogram.

@@

To this end, we develop a sensor fusion strategy that processes the ordinal depth computed by a monocular depth estimator to be consistent with the measurements captured by the diffused SPAD. We demonstrate in extensive simulations that our approach achieves substantial improvements in the quality of the estimated depth maps, regardless of which specific depth estimator is used. Moreover, we build an RGB-SPAD camera prototype and demonstrate in practice that our sensor fusion strategy achieves significantly higher-quality depth maps for a variety of captured scenes compared to MDE alone. With this work, we present a practical way to disambiguate depth estimation with RGB images using minimal additional sensing hardware. Specifically, we make the following contributions:
%
\begin{itemize}
	\item We introduce the idea of augmenting an RGB camera with a global depth histogram captured by a SPAD to address scale ambiguity error in monocular depth estimators.	
  \item We analyze this approach on indoor scenes using the NYU Depth v2 dataset and demonstrate that our approach is able to resolve scale ambiguity while being fast and easy to implement.
	\item We build a prototype RGB-SPAD camera and evaluate its efficacy on captured data, assessing both the quality and the ability of our method to help generalization of monocular depth estimators across scene types. 
\end{itemize}

### 2019-10-18 paper/cvpr2020/sections/related.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
%
Estimating a depth map from a single RGB image has been approached using Markov Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural networks have been applied to this problem. For example, Eigen et al.~\cite{Eigen2014} use a multi-scale neural network to
predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic depth discretization scheme with an ordinal regression loss function. Various experiments using different types of encoder networks (e.g. ResNet, DenseNet)~\cite{Laina2016,Alhashim2018} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Xu2018,Hao2018}. Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of monocular depth estimation using cross-dataset transfer.

Despite achieving remarkable success on estimating ordinal depth from a single image, none of these methods are able to resolve inherent scale ambiguity in a principled manner. We introduce a new approach that leverages existing monocular depth estimation networks but disambiguates their output with depth histogram-like measurements obtained from a single, diffused SPAD. Other approaches to disambiguating monocular depth estimation, for example using optimized freeform lenses~\cite{Wu:2019,Chang:2019:DeepOptics3D} or dual-pixel sensors~\cite{Garg:2019}, these approaches require custom lenses or sensors and specialized image reconstruction methods. In contrast, our diffused SPAD can simply be added to an existing camera, as it is on many cellphones already, and it does not require the standard camera ISP to be changed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Depth Imaging and Sensor Fusion with SPADs}
%
Emerging single-photon LiDAR systems use single photon avalanche diodes (SPADs) to record the time of flight of individual photons. Whereas SPAD detectors can be fabricated using standard CMOS processes, the required picosecond-accurate time-stamping electronics are challenging to miniaturize and fabricate at low cost. For this reason, many single-photon 3D imaging approaches use a single SPAD combined with a raster scanning mechanism~\cite{Lamb2010,Kirmani:2014,pawlikowska2017single,Li:2019}. Unfortunately, this makes it challenging to scan dynamic scenes at high resolution and scanners can also be expensive, difficult to calibrate, and prone to mechanical failure. To reduce the scanning complexity to one dimension, 1D SPAD arrays have been developed~\cite{burri2016linospad,burri2017linospad,OToole2017}, and 2D SPAD arrays are also an active area of research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet, single-pixel SPADs remain the only viable option for low cost consumer devices today.

The proposed method uses a single-pixel SPAD, but rather than aiming it at one point in the scene as proximity sensors do, we propose to diffuse it along with the pulsed light source. This is a unique configuration that allows us capture a transient that closely resembles the shape of the depth histogram of the scene. We develop a sensor fusion algorithm to combine the output of a monocular depth estimator and this depth histogram to achieve more reliable absolute depth estimation. While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018}, in that work an intensity image was primarily used to guide a denoising and upsampling step of recorded 2D SPAD array.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Histogram Matching and Global Hints}
%
Histogram matching is a well-known image processing technique for adjusting an image so that its histogram matches some pre-specified histogram (often derived from another image)~\cite{gonzales1977gray,Gonzalez2008}. Nikolova et al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the image pixels that allows an exact histogram match to be obtained. Morovic et al.~\cite{Morovic2002} provide a simple and concise method that also achieves an exact histogram match while being very fast. In the image reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram to form an image prior based on the Wasserstein distance for image denoising and inpainting. Rother et al.~\cite{Rother2006} use a histogram prior to create an energy function that penalizes foreground segmentations with dissimilar histograms. In a slightly different vein, Zhang et al.~\cite{Zhang2017} train a neural network to produce realistically colorized images given only a black-and-white image and a histogram of global color information.

Because the single SPAD produces a weighted histogram of the depth map, we adapt
the algorithm in Morovic et al. to accommodate general per-pixel
weights, which allows us to compensate for different scene reflectances during
the histogram matching.
% \textcolor{red}{Our method is essentially a modified form of the algorithm in \cite{Morovic2002}, modified for our particular use case. Also worth noting is the fact that most algorithms compute histograms from existing images, whereas our method mesaures the depth histogram indirectly using photon arrivals.} Note: this paragraph needs more work. We can say something like ``Inspired by Morovic et al., we do something'' but then we also need to highlight how our method is different. Perhaps concisely summarize how you adapt it for our SPAD model.
%
% \begin{itemize}
%   \item Exact histogram matching paper used in this work
%   \item Wasserstein-based optimization techniques for
%     histogram-based regularization
% \end{itemize}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Monocular Depth Estimation}
%
Estimating a depth map from a single RGB image has been approached using Markov Random Fields~\cite{Saxena2006}, geometric approaches~\cite{Hoiem2005}, and non-parametric, SIFT-based methods~\cite{Karsch2014}. More recently, deep neural networks have been applied to this problem. For example, Eigen et al.~\cite{Eigen2014} use a multi-scale neural network to
predict depth maps, Godard et al.~\cite{Godard2017} use an unsupervised approach that trains a network using stereo pairs, and Fu et al.~\cite{Fu2018} combine a logarithmic depth discretization scheme with an ordinal regression loss function. Various experiments using different types of encoder networks (e.g. ResNet, DenseNet)~\cite{Alhashim2018,Laina2016} have also been employed with some success, as have approaches mixing deep learning with conditional random fields~\cite{Xu2017}, and attention-based approaches~\cite{Hao2018,Xu2018}. Recently, Lasinger et al.~\cite{Lasinger:2019} improved the robustness of monocular depth estimation using cross-dataset transfer.

Despite achieving remarkable success on estimating ordinal depth from a single image, none of these methods are able to resolve inherent scale ambiguity in a principled manner. We introduce a new approach that leverages existing monocular depth estimation networks and disambiguates the output using depth histogram-like measurements obtained from a single, diffused SPAD. Other approaches to disambiguating monocular depth estimation use optimized freeform lenses~\cite{Chang:2019:DeepOptics3D,Wu:2019} or dual-pixel sensors~\cite{Garg:2019}, but these approaches require custom lenses or sensors and specialized image reconstruction methods. In contrast, our approach is potentially compatible with existing camera systems (\eg deployed on current cell phones) and our algorithms could be used in tandem with existing camera ISPs.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Depth Imaging and Sensor Fusion with SPADs}
%
Emerging single-photon LiDAR systems use single-photon avalanche diodes (SPADs) to record the time of flight of individual photons. SPAD detectors can be fabricated using standard CMOS processes, but the required picosecond-accurate time-stamping electronics are challenging to miniaturize and fabricate at low cost. For this reason, many single-photon 3D imaging approaches use a single SPAD combined with a raster scanning mechanism~\cite{Kirmani:2014,Lamb2010,Li:2019,pawlikowska2017single}. Unfortunately, this makes it challenging to scan dynamic scenes at high resolution and scanners can also be expensive, difficult to calibrate, and prone to mechanical failure. To reduce the scanning complexity to one dimension, 1D SPAD arrays have been developed~\cite{burri2017linospad,burri2016linospad,OToole2017}, and 2D SPAD arrays are also an active area of research~\cite{Niclass2005,Stoppa2007,Veerappan2011,Zhang2018}. Yet, single-pixel SPADs remain the only viable option for low-cost consumer devices today.

The proposed method uses a single-pixel SPAD and pulsed light source that are diffused across the entire scene instead of aimed at a single point, as with proximity sensors. This unique configuration captures a measurement that closely resembles the depth histogram of the scene. Our sensor fusion algorithm achieves reliable absolute depth estimation by combining the SPAD measurement with the output of a monocular depth estimator using a histogram matching technique. While other recent work also explored RGB-SPAD sensor fusion~\cite{Lindell2018}, the RGB image was primarily used to guide the denoising and upsampling of measurements from a SPAD array.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\paragraph{Histogram Matching and Global Hints}
%
Histogram matching is a well-known image processing technique for adjusting an image so that its histogram matches some pre-specified histogram (often derived from another image)~\cite{gonzales1977gray,Gonzalez2008}. Nikolova et al.~\cite{Nikolova2013} use optimization to recover a strict ordering of the image pixels, yielding an exact histogram match. Morovic et al.~\cite{Morovic2002} provide an efficient and precise method for fast histogram matching which supports weighted pixel values. In the image reconstruction space, Swoboda and Schn\"orr~\cite{Swoboda2013} use a histogram to form an image prior based on the Wasserstein distance for image denoising and inpainting. Rother et al.~\cite{Rother2006} use a histogram prior to create an energy function that penalizes foreground segmentations with dissimilar histograms. In a slightly different application area, Zhang et al.~\cite{Zhang2017} train a neural network to produce realistically colorized images given only a black-and-white image and a histogram of global color information.

In our procedure, the diffused SPAD measurements capture a histogram of the depth map where the histogram values are weighted by spatially varying scene reflectances and inverse-square falloff effects. We therefore adapt the algorithm in Morovic et al.~\cite{Morovic2002} in order to accommodate general per-pixel weights during histogram matching.

% \textcolor{red}{Our method is essentially a modified form of the algorithm in \cite{Morovic2002}, modified for our particular use case. Also worth noting is the fact that most algorithms compute histograms from existing images, whereas our method mesaures the depth histogram indirectly using photon arrivals.} Note: this paragraph needs more work. We can say something like ``Inspired by Morovic et al., we do something'' but then we also need to highlight how our method is different. Perhaps concisely summarize how you adapt it for our SPAD model.
%
% \begin{itemize}
%   \item Exact histogram matching paper used in this work
%   \item Wasserstein-based optimization techniques for
%     histogram-based regularization
% \end{itemize}

### 2019-10-18 paper/cvpr2020/sections/simulation.tex

\begin{figure*}[!t]
\begin{center}
\input{sections/figures/sim_table.tex}
\caption{Quantitative evaluation using NYU Depth v2. Bold indicates best performance for that metric, while underline indicates second best. The proposed scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or even outperforms the median rescaling scheme and histogram matching with the exact depth map histogram, even though these methods have access to ground truth. }
\end{center}
\end{figure*}

\begin{figure*}[!t]
  \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.png}
  \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.png}
  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
  \caption{Simulated results from NYU v2 computed with the DenseDepth CNN. The depth maps estimated by the CNN are reasonable, but contain systematic error. Oracle access to the ground truth depth maps, either through the median depth or the depth histogram, can remove this error and correct the depth maps. The proposed method uses a single diffused SPAD and does not rely on ground truth depth, but it achieves a quality that closely matches the best-performing oracle.}
	\label{fig:results_simulated}
\end{figure*}

@@

We use the NYU Depth v2 dataset to evaluate our method. This dataset consists of 249~training and 215~testing scenes of RGB-D data captured using a Microsoft Kinect. \textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}

@@

We show an extensive quantitative evaluation in Table~1. Here, we evaluate three recent monocular depth estimation techniques: DORN~\cite{Fu2018}, DenseDepth~\cite{Alhashim2018}, and MiDaS~\cite{Lasinger:2019}. To evaluate the quality of DORN and DenseDepth, we report various standard error metrics. Moreover, we show a simple post-processing step that rescales their outputs by the median ground truth depth~\cite{Alhashim2018}. We also show the results of histogram matching the output of the CNNs with the ground truth depth map histogram. Note that we do not report the quality of the direct output of MiDaS as this algorithm does not output metric depth. However, we do show its output histogram matched with the ground truth depth map histogram. In all cases, post-processing the estimated depth maps either with the median depth or depth histogram significantly improves the absolute depth estimation, often by a large margin compared to the raw output of the CNNs. Unfortunately, ground truth depth is typically not accessible so neither of these two post-processing methods are viable in practical application scenarios.

We simulate the measurements of a single diffused SPAD as discussed in Section~\ref{sec:method} and also add Poisson noise and background signal. In table~1, results are shown for several different signal-to-background ratios (SBRs). We see that the proposed method achieves high-quality results for correcting the raw depth map estimated by the respective CNNs for all cases. The quality of the resulting depth maps is almost as good as that achieved with the oracle ground truth histogram, which can be interpreted as an approximate upper bound on the performance, despite a relatively high amount of noise and background signal. These results demonstrate that the proposed method is agnostic to the specific depth estimation CNN applied to get the initial depth map and that it generally achieves significant improvements in the estimated depth maps, clearly surpassing the variation of performance between depth estimation CNNs.

In Figure~\ref{fig:results_simulated}, we also show qualitative results of our simulations. For each of these scenes, we show the RGB reference image, the ground truth depth map, the raw output of the DenseDepth CNN, the result of rescaling the CNN output by the median ground truth depth, the result of histogram-matching the CNN output by the ground truth depth map histogram, and the result achieved by the proposed method for an SBR of 100. Error maps for all the depth estimation methods are shown. As expected, the CNN outputs depth maps that look reasonable but that have an average root mean squared error (RMSE) of about 50--60~cm. Re-scaling this depth map by the median ground truth depth value slightly improves the quality and histogram-matching it with the ground truth depth histogram improves the depth map a lot. The quality of the proposed method is close to that using the oracle histogram, despite relying on noisy SPAD measurements. Additional simulations using DenseDepth and other depth estimation CNNs for a variety of scenes are shown in the supplement.

>>>>

\begin{table*}[!t]
\begin{center}
\input{sections/figures/sim_table.tex}
\caption{Quantitative evaluation using NYU Depth v2. Bold indicates best
performance for that metric, while underline indicates second best. The proposed
scheme outperforms DenseDepth and DORN on all metrics, and it closely matches or
even outperforms the median rescaling scheme and histogram matching with the
exact depth map histogram, even though those methods have access to ground truth. }
\label{tab:comparison}
\end{center}
\end{table*}

\begin{figure*}[!h]
  % \includegraphics[width=\textwidth]{comparison/densedepth_468_comparison.pdf}
  % \includegraphics[width=\textwidth]{comparison/densedepth_194_comparison.pdf}
  \includegraphics[width=\textwidth]{comparison.pdf}
  %\includegraphics[width=\textwidth]{comparison/densedepth_258_comparison.png}
  \caption{Simulated results from NYU v2 computed with the DenseDepth
  CNN~\cite{Alhashim2018}. The depth maps estimated by the CNN are reasonable,
  but contain systematic error. Oracle access to the ground truth depth maps,
  either through the median depth or the depth histogram, can remove this error
  and correct the depth maps. The proposed method uses measurements from a single diffused SPAD and does not rely on ground truth depth, but it achieves a quality that closely matches the best-performing oracle.}
	\label{fig:results_simulated}
\end{figure*}

@@

We use the NYU Depth v2 dataset to evaluate our method. This dataset consists of
249~training and 215~testing scenes with RGB-D images captured using a Microsoft
Kinect.

To simulate a SPAD histogram, we take the provided depth map and 
calculate a weighted depth histogram by weighting the pixel contributions to
each depth bin by the luminance of each pixel. To model radiometric falloff, we
multiply each bin by $1/z^2$, and convolve with a modeled system temporal
response, which we approximate as a Gaussian with a full-width at half-maximum of 70ps. We scale
the histogram by the total number of observed signal photon counts (set to 
$10^6$) and  add a fixed number of background photons $b \in \set{10^5, 2\times
10^4, 10^4}$. The background counts are evenly distributed across all bins to simulate the ambient and dark
count detections, and the different background levels correspond to
signal-to-background ratios (SBR) of $10, 50$ and $100$ respectively. Finally,
each bin is Poisson sampled to produce the final simulated SPAD transient.

% \textcolor{red}{Need more details: how did you simulate the SPAD measurements from this: discuss albedo, square distance falloff, Poisson noise, background, number of SPAD bins, define what SBR is etc.}

@@

We show an extensive quantitative evaluation in Table~\ref{tab:comparison}. Here, we evaluate three recent monocular depth estimation techniques: DORN~\cite{Fu2018}, DenseDepth~\cite{Alhashim2018}, and MiDaS~\cite{Lasinger:2019}. To evaluate the quality of DORN and DenseDepth, we report various standard error metrics. Moreover, we show a simple post-processing step that rescales their outputs by the median ground truth depth~\cite{Alhashim2018}. We also show the results of histogram matching the output of the CNNs with the ground truth depth map histogram. Note that we do not report the quality of the direct output of MiDaS as this algorithm does not output metric depth. However, we do show its output histogram matched with the ground truth depth map histogram. In all cases, post-processing the estimated depth maps either with the median depth or depth histogram significantly improves the absolute depth estimation, often by a large margin compared to the raw output of the CNNs. Unfortunately, ground truth depth is typically not accessible so neither of these two post-processing methods are viable in practical application scenarios.

Instead, our method uses the simulated measurements from a single diffused SPAD
to correct the depth map. In Table~\ref{tab:comparison}, results are shown for several different
signal-to-background ratios (SBRs). We see that the proposed method achieves
high-quality results for correcting the raw depth map estimated by the
respective CNNs for all cases. The quality of the resulting depth maps is almost
as good as that achieved with the oracle ground truth histogram, which can be
interpreted as an approximate upper bound on the performance, despite a
relatively high amount of noise and background signal. These results demonstrate
that the proposed method is agnostic to the specific depth estimation CNN
applied to get the initial depth map and that it generally achieves significant
improvements in the estimated depth maps, clearly surpassing the variation in
performance between depth estimation CNNs.

In Figure~\ref{fig:results_simulated}, we also show qualitative results of our
simulations. For each of these scenes, we show the RGB reference image, the
ground truth depth map, the raw output of the DenseDepth CNN, the result of
rescaling the CNN output by the median ground truth depth, the result of
histogram-matching the CNN output by the ground truth depth map histogram, and
the result achieved by the proposed method for an SBR of 100. Error maps for all
the depth estimation methods are shown. As expected, the CNN outputs depth maps
that look reasonable but that have an average root mean squared error (RMSE) of
about 50--60~cm. Re-scaling this depth map by the median ground truth depth
value slightly improves the quality and histogram-matching with the ground
truth depth histogram shows a large amount of improvement. The quality of the
proposed method is close to using the oracle histogram, despite relying on
noisy SPAD measurements. Additional simulations using DenseDepth and other depth
estimation CNNs for a variety of scenes are shown in the supplement.
